%!TEX program = xelatex
\documentclass[letterpaper,12pt]{exam}
\usepackage{../videoNotes}
\usepackage{xcolor}
\usepackage[dvipsnames]{xcolor}


\newcommand{\unit}{Unit 08}
\pagestyle{headandfoot}
\firstpageheader{CSC 187 \semester\ \  \unit}{}{Name: $\rule{6cm}{0.15mm}$}
\runningheader{CSC 187 \semester}{\unit}{Page \thepage\ of \numpages}
\firstpagefooter{}{}{}
\runningfooter{}{}{}

\begin{document}
\section*{\unit\_010 -- Shortcut Assignment Operators} % Unnumbered section
\par{\fontfamily{qzc}\selectfont\textbf{Video Length 10:00}}

\begin{questions}
\begin{samepage}
    \question Rewrite each of the following using the shortcut assignment operators.
      \begin{itemize}
        \item \code{n = n +1;}
        \vspace{5mm}
        \item \code{count = count - 2;}
        \vspace{5mm}
        \item \code{number = number * 2;}
        \vspace{5mm}
        \item \code{i = i / 2;}
        \vspace{5mm}
        \item \code{q = 5 + q;}
        \vspace{5mm}
       \end{itemize}
\end{samepage}

\begin{samepage}
    \question Which of the shortcut operators in this unit is used most often.
    \vspace{5mm}
\end{samepage}


\section*{\unit\_020 -- Shortcut Operators Gone Wild!} % Unnumbered section
\par{\fontfamily{qzc}\selectfont\textbf{Video Length 24:03}}

\begin{samepage}
    \question Rewrite the following statements using the increment and decrement operators.
      \begin{itemize}
        \item \code{i += 1;}
        \vspace{5mm}
        \item \code{count -= 1;}
        \vspace{5mm}
       \end{itemize}
\end{samepage}

\begin{samepage}
    \question Rewrite the following statements using the increment and decrement operators. \textbf{\emph{But this time use two different increment and decrement operators.}}
      \begin{itemize}
        \item \code{i += 1;}
        \vspace{5mm}
        \item \code{count -= 1;}
        \vspace{5mm}
       \end{itemize}
\end{samepage}

\begin{samepage}
    \question In your own words, describe the difference between prefix and postfix operators.
    \vspace{25mm}
\end{samepage}

\begin{samepage}
    \question What is a side effect in programming?
    \vspace{5mm}
\end{samepage}

\begin{samepage}
    \question What would be printed by the following loop?
    \begin{verbatim}
    int i = 0;
    while(i < 5){
        System.out.print(i++);
    }
    \end{verbatim}
    \vspace{5mm}
\end{samepage}

\begin{samepage}
    \question What are two ways to protect your code from unintended side effects when using increment and decrement operators?
      \begin{itemize}
        \item [$\rightarrow$]
        \vspace{5mm}
        \item [$\rightarrow$]
        \vspace{5mm}
           \end{itemize}
\end{samepage}

\begin{samepage}
    \question What is the practical difference between i++ and ++i whe the increment operators are the only items in the statement?  (trick question)
    \vspace{5mm}
\end{samepage}

\begin{samepage}
    \question The beginning of the video made it look like the increment operator was just a short cut for the +=1 operation.  Explain why the increment and decrement operators are not really just shortcuts of shortcuts.  (This is not discussed explicitly in the videos, so you may need to think about it.)
    \vspace{5mm}
\end{samepage}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{samepage}
    \begin{center}
    \rule{0.8\textwidth}{.4pt}
    \end{center}
	\question Comment or ask questions here if there are any issues you would like for the instructor to address.  It is not necessary to answer if you do not have questions.
	\vspace{30mm}
\end{samepage}

\end{questions}

\end{document}