
%!TEX program = xelatex
\documentclass[letterpaper,12pt]{exam}
\usepackage{../videoNotes}
\usepackage{xcolor}
\usepackage[dvipsnames]{xcolor}
\usepackage{soul}

\newcommand{\unit}{Unit 10}
\pagestyle{headandfoot}
\firstpageheader{CSC 187 \semester\ \  \unit}{}{Name: $\rule{6cm}{0.15mm}$}
\runningheader{CSC 187 \semester}{\unit}{Page \thepage\ of \numpages}
\firstpagefooter{}{}{}
\runningfooter{}{}{}

\begin{document}
\section*{\unit\_010.010 -- The Object Class} 
\par{\fontfamily{qzc}\selectfont\textbf{Video Length 13:20}}
\begin{questions}
\begin{samepage}
    \question Why is the Object class important?
    \vspace{5mm}
\end{samepage}
\begin{samepage}
    \question What does the .toString() method do?  Why is it considered a "magic method?"
    \vspace{5mm}
\end{samepage}

\begin{samepage}
    \question What data type does the .hashCode() method return?
    \vspace{5mm}
\end{samepage}

\begin{samepage}
    \question What data type does the .equals() method return?  How does the .equals() method relate to the .hashCode() method?
    \vspace{5mm}
\end{samepage}

%----------------------------------
\section*{\unit\_010.020 -- The Namespace Problem} 
\par{\fontfamily{qzc}\selectfont\textbf{Video Length 8:28 }}

\begin{samepage}
    \question What is a Namespace?
    \vspace{5mm}
\end{samepage}

\begin{samepage}
    \question Why can variables have the same name in different methods?
    \vspace{5mm}
\end{samepage}

\begin{samepage}
    \question When is it OK for two methods to have the same name (and signature)?
    \vspace{5mm}
\end{samepage}

%----------------------------------
\section*{\unit\_010.030 -- Packages and Classes} 
\par{\fontfamily{qzc}\selectfont\textbf{Video Length 14:15}}

\begin{samepage}
    \question In the following url, "woz" is the name of a server.  Identify the TLD, SLD, and the subdomain.
    \begin{verbatim}
              https://woz.csmp.missouriwestern.edu
    \end{verbatim}
    \vspace{5mm}
\end{samepage}

\begin{samepage}
    \question Suppose you work for a company that used the subdomain code.ajax.com.  How would you start the package names for your company?
    \vspace{5mm}
\end{samepage}


%----------------------------------
\section*{\unit\_010.040 -- Creating a Class} 
\par{\fontfamily{qzc}\selectfont\textbf{Video Length 5:15}}

\begin{samepage}
    \question What is the base name for packages you create in this course?
    \vspace{5mm}
\end{samepage}

\begin{samepage}
    \question What file do you right-click on in order to make a package in the current project?
    \vspace{5mm}
\end{samepage}


%----------------------------------
\section*{\unit\_050 -- Objects with Fields and toString()} 
\par{\fontfamily{qzc}\selectfont\textbf{Video Length 14:20}}

\begin{samepage}
    \question Are the variables representing the fields declared inside a method?
    \vspace{5mm}
\end{samepage}

\begin{samepage}
    \question Are the fields declared static?
    \vspace{5mm}
\end{samepage}

\begin{samepage}
    \question Is the toString() method static?
    \vspace{5mm}
\end{samepage}
\begin{samepage}
    \question What is the return type of the toString method?
    \vspace{5mm}
\end{samepage}
\begin{samepage}
    \question What are the parameters of the toString method (trick question!)
    \vspace{5mm}
\end{samepage}
\begin{samepage}
    \question Does the toString() method print?
    \vspace{5mm}
\end{samepage}
\begin{samepage}
    \question Is it normal to put a \\n at the end of the string that is returned by toString()?
    \vspace{5mm}
\end{samepage}
\begin{samepage}
    \question What String method may be used to format the output for the String
    \vspace{5mm}
\end{samepage}


%----------------------------------
\section*{\unit\_010.055 -- Users} 
\par{\fontfamily{qzc}\selectfont\textbf{Video Length  8:35}}

\begin{samepage}
    \question In the context of this course, who is the "User?"
    \vspace{5mm}
\end{samepage}

%----------------------------------
\section*{\unit\_010.060 -- Setters} 
\par{\fontfamily{qzc}\selectfont\textbf{Video Length 13:05}}

\begin{samepage}
    \question What does the reserved word "this" mean in Java?
    \vspace{5mm}
\end{samepage}

\begin{samepage}
    \question Assume that we added a field called "capital" which is a string.  Write the setter needed for the capital field.  You do not need to do any error checking.  Be sure your method meets all the criteria on the left. (The items on the left may also be the basis of test questions.)
    \begin{itemize}
        \item the setter is public
        \item the setter is NOT static
        \item the setter returns void
        \item the name starts with set
        \item the name ends with the field name
        \item the parameter is the same type as the field
        \item the parameter has the same name as the field
        \item \texttt{\textbf{this}} identifies the class variable
    \end{itemize}
    \vspace{5mm}
\end{samepage}

%----------------------------------
\section*{\unit\_010.070 -- Getters} 
\par{\fontfamily{qzc}\selectfont\textbf{Video Length 2:20}}
\begin{samepage}
    \question Assume that we added a field called "capital" which is a string.  Write the getter needed for the capital field.  Be sure your method meets all the criteria on the left. (The items on the left may also be the basis of test questions.)
    \begin{itemize}
        \item the getter is public
        \item the getter is NOT static
        \item the getter returns data type of the field
        \item the name starts with get
        \item the name ends with the field name
        \item there is no parameter
        \item the body of the method is probably a single return statement.
    \end{itemize}
    \vspace{5mm}
\end{samepage}

%----------------------------------
\section*{\unit\_010.080 -- Constructors} 
\par{\fontfamily{qzc}\selectfont\textbf{Video Length 15:20}}
\begin{samepage}
    \question Answer each of the following regarding contructors:
      \begin{itemize}
        \item Should constructors be public (yes/no)
        \vspace{5mm}
        \item What is the return type of a constructor? \rule{20mm}{0.35mm} (warning: This is a \st{trick} technical question.)
        \vspace{5mm}
        \item Constructors must be named like the name of the class, including capitalization. yes or no
        \vspace{5mm}
        \item If the programmer does not specify a constructor, what happens?
        \vspace{15mm}
        \item If the programmer specifies a constructor, is the noarg constructor supplied by java? yes or no
        \vspace{5mm}
       \end{itemize}
\end{samepage}

\begin{samepage}
    \question What is the "noArg constructor?"
    \vspace{5mm}
\end{samepage}

\begin{samepage}
    \question Suppose there is a constructor defined as follows.  Write the constructor that sets only a name, and sets the distance to Double.POSITIVE\_INFINITY
    \begin{verbatim}
            public Star(String name, double distance)\{...\}
    \end{verbatim}
    \vspace{5mm}
\end{samepage}


%----------------------------------
\section*{\unit\_010.85 -- Java Bean} 
\par{\fontfamily{qzc}\selectfont\textbf{Video Length 5:10}}
\begin{samepage}
    \question Does a Java Bean need a default constructor?  
    \vspace{5mm}
\end{samepage}

%----------------------------------
\section*{\unit\_010.090 -- JavaDoc} 
\par{\fontfamily{qzc}\selectfont\textbf{Video Length 5:15}}

Not much to ask questions here.  Just don't forget the JavaDoc!

%----------------------------------
\section*{\unit\_010.100 -- Array of Objects } 
\par{\fontfamily{qzc}\selectfont\textbf{Video Length 17:30}}

This video and the next one will be important for this week's assignment.

\begin{samepage}
    \question Write the code needed to create an array of Widgets.  Assume there is a constant called MAX\_WIDGETS. (Your answer should just be one line of code with a couple of pairs of square brackets in it.)
    \vspace{5mm}
\end{samepage}

\begin{samepage}
    \question Write a complete method needed to print an array of widgets.  Assume there are n widgets in the array.
    \vspace{55mm}
\end{samepage}

%----------------------------------
\section*{\unit\_010.110 -- Finding the maximum} 
\par{\fontfamily{qzc}\selectfont\textbf{Video Length 9:32}}

\begin{samepage}
    \question The assignment asked you to find the maximum value.  Write a method to find the minimum?  Circle the changes you needed to make.
    \vspace{55mm}
\end{samepage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Please write any lingering questions you have here.
\end{questions}

\end{document}