%!TEX program = xelatex
\documentclass[letterpaper,12pt]{exam}
\usepackage{../videoNotes}
\usepackage{xcolor}
\usepackage[dvipsnames]{xcolor}

\newcommand{\unit}{Unit 04}
\pagestyle{headandfoot}
\firstpageheader{CSC 187 \semester\ \  \unit}{}{Name: $\rule{6cm}{0.15mm}$}
\runningheader{CSC 187 \semester}{\unit}{Page \thepage\ of \numpages}
\firstpagefooter{}{}{}
\runningfooter{}{}{}

\begin{document}

\begin{questions}

\section*{\unit\_005 --- Methods} % Unnumbered section

\begin{samepage}
	\question Why do method names often include verbs?
	\vspace{5mm}
\end{samepage}

\begin{samepage}
	\question What are 4 advantages of using methods?
	  \begin{itemize}
		\item 
		\vspace{5mm}
		\item 
		\vspace{5mm}
		\item 
		\vspace{5mm}
		\item 
		\vspace{5mm}
	   \end{itemize}
\end{samepage}

\begin{samepage}
	\question Is it better to have large, powerful and complex methods, or is it better to have methods that do one thing?
	\vspace{5mm}
\end{samepage}

\section*{\unit\_010} % Unnumbered section

\begin{samepage}
	\question What does "public" mean in the declaration of the method?
	\vspace{5mm}
\end{samepage}

\begin{samepage}
	\question What does the \code{void} stand for?
	\vspace{5mm}
\end{samepage}

\begin{samepage}
	\question Can a method call another method?
	\vspace{5mm}
\end{samepage}
\begin{samepage}
	\question Can a method call itself?  Is that a good idea?
	\vspace{5mm}
\end{samepage}

\section*{\unit\_020 Method returning value} % Unnumbered section
\begin{samepage}
	\question What extra statement do methods that return a value have that void methods do not need to have?
	\vspace{5mm}
\end{samepage}

\clearpage

\begin{samepage}
	\question Write a method that returns the day of the current month.  You will need to look at the LocalDate API methods to find the method that returns the date.  Use the model program in the video to find the date.  Return the day of the month rather than the year.  Be sure to update the local variable so the name is appropriate for a day.  You might want to try coding this in IntelliJ.  
	\vspace{55mm}
\end{samepage}

\section*{\unit\_023 Scope and Local Variables} % Unnumbered section
\begin{samepage}
	\question What does "Scope" mean?
	\vspace{5mm}
\end{samepage}
\begin{samepage}
	\question A "Local Variable" is one that is declared inside
	  \begin{itemize}
		\item 
		\vspace{5mm}a class
		\item 
		\vspace{5mm}a method
	   \end{itemize}
\end{samepage}
\section*{\unit\_025 Parameters and Argument} % Unnumbered section

\begin{samepage}
	\question What is the difference between an argument and a parameter?
	\vspace{5mm}
\end{samepage}
\begin{samepage}
	\question If there are more than two arguments, does the order of the arguments matter?
	\vspace{5mm}
\end{samepage}
\begin{samepage}
	\question Do arguments and parameters need to have the same name? 
	\vspace{5mm}
\end{samepage}

\section*{\unit\_027 Method Signature} % Unnumbered section
\begin{samepage}
	\question Circle the items that are part of the method signature
	  \begin{itemize}
		\item return type
		\vspace{5mm}
		\item method name
		\vspace{5mm}
		\item data types of parameters
		\vspace{5mm}
		\item variable names of parameters
		\vspace{5mm}
	   \end{itemize}
\end{samepage}

\begin{samepage}
	\question Can a class have two different methods with the same name?  Explain your answer.
	\vspace{5mm}
\end{samepage}
\begin{samepage}
	\question Can a class have two different methods with the same signature?  This was not explained in the video, so you will need to think about it.  Why can't two different methods have the same signature if they are in the same class?
	\vspace{5mm}
\end{samepage}
\section*{\unit\_030 JavaDoc Comments} % Unnumbered section
\begin{samepage}
	\question How is the syntax of a JavaDoc Comment different than the syntax of a Block comment?
	\vspace{5mm}
\end{samepage}
\begin{samepage}
	\question Write the entire JavaDoc comment for the following method (only the first line of the method is shown.  Be sure to write the javadoc comment above the first line) The method calculates the hypotenuse of a right triangle given the two sides.
	\vspace{5mm}
	\begin{verbatim}
		






		pubic static void double calculateHypoteneuse(double a, double b)
	\end{verbatim}
\end{samepage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{samepage}
	\question Do you have any other questions?
	\vspace{30mm}
\end{samepage}

\end{questions}

\end{document}