%!TEX program = xelatex
\documentclass[letterpaper,12pt]{exam}
\usepackage{../videoNotes}
\usepackage{xcolor}
\usepackage[dvipsnames]{xcolor}

\newcommand{\unit}{Unit 03}
\pagestyle{headandfoot}
\firstpageheader{CSC 187 \semester\ \  \unit}{}{Name: $\rule{6cm}{0.15mm}$}
\runningheader{CSC 187 \semester}{\unit}{Page \thepage\ of \numpages}
\firstpagefooter{}{}{}
\runningfooter{}{}{}

\begin{document}

\begin{questions}

\section*{\unit\_010 --- printf} % Unnumbered section

\begin{samepage}
	\question What format code does Printf use for each of the following data types?
	  \begin{itemize}
		\item \code{integers}
		\vspace{5mm}
		\item \code{real numbers}
		\vspace{5mm}
		\item \code{Strings}
		\vspace{5mm}
		\item \code{characters}
		\vspace{5mm}
	   \end{itemize}
\end{samepage}
\begin{samepage}
	\question Does the printf method automatically include a newline character?
	\vspace{5mm}
\end{samepage}
\begin{samepage}
	\question Assume there are variables \code{length} and \code{width} and a double variable named \code{area}.  Write the full System.out.printf() statement that prints the following statement.  Fill in the blanks with the length, width, and area.  Make sure you include a newline.
	\begin{verbatim}
		A rectangle with a length of ____ and a width of ____ has an area of ______.
	\end{verbatim}

	\vspace{5mm}
\end{samepage}
\section*{\unit\_020 Characters and Strings} % Unnumbered section
\begin{samepage}
	\question In Java, is a \code{char} the same as a \code{String}?  Explain the difference.
	\vspace{5mm}
\end{samepage}
\begin{samepage}
	\question In Java, what is the difference between single quotes and double quotes?  Is \code{'B'} and \code{"B"} the same?
	\vspace{5mm}
\end{samepage}

\begin{samepage}
	\question Is '\symbol{92}n' one characters or two?
	\vspace{5mm}
\end{samepage}

\begin{samepage}
	\question What are "ASCII Codes?"
	\vspace{5mm}
\end{samepage}
\begin{samepage}
	\question What are the ASCII codes less than 32 called?
	\vspace{5mm}
\end{samepage}
\begin{samepage}
	\question 
	  \begin{itemize}
		\item ' ' (space) \rule{20mm}{0.15mm}
		\vspace{5mm}
		\item '0' (zero) \rule{20mm}{0.15mm}
		\vspace{5mm}
		\item '@' \rule{20mm}{0.15mm}
		\vspace{5mm}
		\item 'A' \rule{20mm}{0.15mm} 
		\vspace{5mm}
		\item 'a' \rule{20mm}{0.15mm}
		\vspace{5mm}
		\item '~' (tilde) \rule{20mm}{0.15mm}
		\vspace{5mm}
	   \end{itemize}
\end{samepage}
\begin{samepage}
	\question What is the biggest problem with ASCII codes?
	\vspace{15mm}
\end{samepage}
\begin{samepage}
	\question How many bits does extended ASCII use?
	\vspace{5mm}
\end{samepage}


\begin{samepage}
	\question Does Java use ASCII or Unicode to represent character data?
	\vspace{5mm}
\end{samepage}

\begin{samepage}
	\question How many bits does Java use to represent type char?
	\vspace{5mm}
\end{samepage}

\begin{samepage}
	\question Is ASCII built into Unicode, or did Unicode start from scratch?
	\vspace{5mm}
\end{samepage}
\section*{\unit\_025 Classes and Objects} % Unnumbered section
\begin{samepage}
	\question What are the 8 "primitive" data types in Java?
	\vspace{5mm}
\end{samepage}
\begin{samepage}
	\question What two things does a class define?
	\vspace{5mm}
\end{samepage}
\begin{samepage}
	\question What is the difference between an object and a class?
	\vspace{5mm}
\end{samepage}
\begin{samepage}
	\question I didn't mention it at this point in the video, but are objects capitalized?
	\vspace{5mm}
\end{samepage}


\begin{samepage}
	\question What is an instance of a class?
	\vspace{5mm}
\end{samepage}

\begin{samepage}
	\question What is the Java API?
	\vspace{5mm}
\end{samepage}

\begin{samepage}
	\question What is a method in Java?
	\vspace{5mm}
\end{samepage}

\begin{samepage}
	\question How do you call a method in Java?
	\vspace{5mm}
\end{samepage}

\begin{samepage}
	\question Suppose you have a string called "sentence."  Write the statment needed to print the number of letters in sentence.
	\vspace{5mm}
\end{samepage}

\section*{\unit\_027 Methods} % Unnumbered section


\begin{samepage}
	\question What is a function?
	\vspace{5mm}
\end{samepage}

\begin{samepage}
	\question What is an "argument?"  Do all functions have arguments?  What happens when a function has more than one argument?
	\vspace{5mm}
\end{samepage}

\begin{samepage}
	\question What is a "method?"  
	\vspace{5mm}
\end{samepage}

\section*{\unit\_03 The String class} % Unnumbered section

\begin{samepage}
	\question How can you determine the return type of a method using the Java API?
	\vspace{5mm}
\end{samepage}
\begin{samepage}
	\question For each of the following, specify the return type and the arguments, if any.
	The last one was not covered in the video.  Look it up for yourself in the API
	  \begin{itemize}
		\item \code{length()} Return:  \rule{20mm}{0.15mm}     Arguments: 
		\vspace{5mm}
		\item \code{charAt()} Return:   \rule{20mm}{0.15mm}     Arguments: 
		\vspace{5mm}
		\item \code{trim()} Return:   \rule{20mm}{0.15mm}      Arguments:
		\vspace{5mm}
		\item \code{toUpperCase()} Return:  \rule{20mm}{0.15mm}       Arguments:
		\vspace{5mm}
		\item \code{subString()} Return:   \rule{20mm}{0.15mm}      Arguments:
		\vspace{5mm}
	\end{itemize}
\end{samepage}

\begin{samepage}
	\question Would this code work?  Try typing it into IntelliJ. What is the answer?  My wife counted 8 characters in the string.  Is that what the output says?  Why is it different?  If it does not work, fix the errors
	\begin{verbatim}
		System.out.println ( "abcdef\n".length() );
	\end{verbatim}
	\vspace{5mm}
\end{samepage}

\section*{\unit\_040 Concatenating Strings} % Unnumbered section

\begin{samepage}
	\question What are the three methods of concatenating strings?  Which is the easiest?
	\vspace{5mm}
\end{samepage}

\begin{samepage}
	\question Suppose you have the following code fragment.  Write the code to concatenate the title, the word "by" and the author.  First, do it with the + method.  Then do it with string format.  Write your code below.  Which one do you think is easier?
	\begin{verbatim}
		String title = "The Raven";
		String author= "Edgar Allen Poe";
		String byline;
	\end{verbatim}
	Write the two lines of code.  Which do you think is better?
	\vspace{25mm}
\end{samepage}
\section*{\unit\_060 Promotion} % Unnumbered section

\begin{samepage}
	\question What is Promotion?  How does Java convert from primitive types to strings?
	\vspace{5mm}
\end{samepage}

\section*{\unit\_070 Mixing int and double} % Unnumbered section

What is the problem with the following statement?  Rewrite the statement and fix the problem.
\begin{verbatim}
	int markup = 3/2;
	double wholesale = 100;
	double retail = wholesale * markup;
	System.out.println(wholesale);
\end{verbatim}
\section*{\unit\_080 Block Comments} % Unnumbered section
\begin{samepage}
	\question Write the /* block comment */ you should put in a program.  For the description, make up a program you think would be interesting but not too hard.  If someone suggests something involving mixed mode arithmetic I might consider using it as a homework assignment.
	\vspace{35mm}
\end{samepage}

\begin{samepage}
	\question What class is normally used to read from the keyboard?
	\vspace{5mm}
\end{samepage}

\begin{samepage}
	\question Do import statements normally go above or below the opening comment for a program?
	\vspace{5mm}
\end{samepage}

\begin{samepage}
	\question What does echo print mean?
	\vspace{5mm}
\end{samepage}

\begin{samepage}
	\question Look at the Scanner API.  What method is used to read each of the following data types?
		  \begin{itemize}
			\item \code{int}
			\vspace{5mm}
			\item \code{double}
			\vspace{5mm}
			\item \code{byte}
			\vspace{5mm}
			\item \code{String}
			\vspace{5mm}
			\item \code{char}
			\vspace{5mm}
		   \end{itemize}
		   Note from the instructor:This question is not really fair on a couple of points.  It seems like the method for String should be .nextString(), but it is not.  The original version of Scanner only read Strings.  Therefore there was no need to have methods for each type.  There was only one .next() method, so it did not need to specify String.

		   The question on char is also flat out mean for me to even ask.  It looks like they never finished all the primitive methods; don't spend too long looking.  
	\end{samepage}
	\clearpage
	\begin{samepage}
		\question Write the code (other than the import) that will read a double from the keyboard.  The program should prompt the user with a message "What is the distance in miles?  Be sure to leave a blank space after the prompt, but leave the cursor on the same like.  Then read the distance from the keyboard.  After reading the data, echo print the distance that you read in.
		\vspace{155mm}
	\end{samepage}
	

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{samepage}
	\question Do you have any other questions?
	\vspace{30mm}
\end{samepage}

\end{questions}

\end{document}